### 2012-03-15 doc/theses/mikula/combination_with_existing_methods_of_inference.tex
Master thesis: In progress.

\chapter{Combination with Existing Methods of Inference}
In this chapter, we describe how to incorporate the inferred statements with existing methods of XML schema inference. We focus on a class of methods which are based on a creation and subsequent simplification of the initial grammar (as discussed in Chapter \ref{chapter_analysis_of_recent_approaches}).

>>>>

\chapter{Combination with Existing Methods of Inference} \label{CHAPTER_combination_with_existings_methods_of_inference}
In this chapter, we describe how to incorporate the inferred statements with existing methods of XML schema inference. We focus on a class of methods which are based on a creation and subsequent simplification of the initial grammar (as discussed in Chapter \ref{chapter_analysis_of_recent_approaches}).

### 2012-03-15 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\chapter{Proposed Algorithm}
In this thesis we are developing an approach dealing with inference of XML schema, which input consists of two components; a set of XML documents and a set of XQuery queries related to the documents. The proposed algorithm introduced in this chapter describes the processing of XQuery queries only and a combination of its output with an existing method of XML schema inference (to produce a complete XML schema) is discussed in the next chapter.

>>>>

\chapter{Proposed Algorithm} \label{CHAPTER_proposed_algorithm}
In this thesis we are developing an approach dealing with inference of XML schema, which input consists of two components; a set of XML documents and a set of XQuery queries related to the documents. The proposed algorithm introduced in this chapter describes the processing of XQuery queries only and a combination of its output with an existing method of XML schema inference (to produce a complete XML schema) is discussed in the next chapter.
